Designing a Search for the BBC

### 2013-08-29 coursework.tex
Did some amendments following proof read.

\section{Rationale}

The BBC has been publishing content on the World Wide Web since the
mid 1990s and since then the amount and the diversity has increased
exponentially. Large websites or indeed the web as a whole would not have
been usable nor useful without the rise in quality of web search engines to
help people find content based on keywords or phases that describe or
appear in the sought after pages.

@@

The purpose of this report is to start the high-level design -- and perhaps
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find equally news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

Checkland \cite{checkland1990soft} decribed a \emph{Rich Picture} approach to
representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in figure~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive the search and discovery of
those websites.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around user's seeking educational
and informative material such as GCSE Bitesize or any other
learning resouces.

>>>>

\section{Background}

The BBC has been publishing content on the World Wide Web since the
mid 1990s and since then the amount and the diversity has increased
exponentially. Large websites -- or indeed the web as a whole --
would not have been usable nor useful without the rise in quality of
web search engines.

@@

The purpose of this report is to start the high-level design -- and perhaps
look at the lower levels of one or two aspects -- of a search application
specific to BBC content. The intent is to provide a consistent user interface
that allows the audience to find news articles, sport results,
TV catch-up, education resources and everything else the BBC produces.

@@

Checkland and Scoles \cite{checkland1990soft} decribed a \emph{Rich Picture} approach
for representing a problem situation early in SSM approaches.
Given the size and complexity of the
search system as a whole, a useful initial step is to create such an informal
representation of what is known about the problem. Figure~\ref{rich-picture}
shows what I know of the audience, search and most BBC online content areas.
Note that not all areas are covered and a strong emphasis is placed on TV
catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
as it shares a lot of similarity with television in terms of use and any
differences are out of scope for this design.

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in figure~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive a search-based discovery of
those websites.

@@

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around users seeking educational
and informative material such as GCSE Bitesize or any other
learning resouces.
